### 2021-01-31 codebook_df.Rmd
prepare data for analysis

---
title: "Codebook created on 2021-01-31 at 2021-01-31 09:50:03"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results = 'asis')
```

A codebook contains documentation and metadata describing the contents, structure, and layout of a data file.

## Dataset description
The data contains 1904 cases and 27 variables.

## Codebook

```{r}
summaries <- read.csv("./codebook_df.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### Legend

* __Name__: Variable name
* __type__: Data type of the variable
* __missing__: Proportion of missing values for this variable
* __unique__: Number of unique values
* __mean__: Mean value
* __median__: Median value
* __mode__: Most common value (for categorical variables, this shows the frequency of the most common category)
* **mode_value**: For categorical variables, the value of the most common category
* __sd__: Standard deviation (measure of dispersion for numerical variables
* __v__: Agresti's V (measure of dispersion for categorical variables)
* __min__: Minimum value
* __max__: Maximum value
* __range__: Range between minimum and maximum value
* __skew__: Skewness of the variable
* __skew_2se__: Skewness of the variable divided by 2*SE of the skewness. If this is greater than abs(1), skewness is significant
* __kurt__: Kurtosis (peakedness) of the variable
* __kurt_2se__: Kurtosis of the variable divided by 2*SE of the kurtosis. If this is greater than abs(1), kurtosis is significant.

This codebook was generated using the [Workflow for Open Reproducible Code in Science (WORCS)](https://osf.io/zcvbs/)

### 2021-01-31 manuscript/manuscript.Rmd
prepare data for analysis

---
title: "Untitled"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <git@github.com:cjvanlissa/MSRC_LPA.git>.

This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-01-31 prepare_data.R

@@ -1,0 +1,15 @@
+# In this file, write the R-code necessary to load your original data file
+# (e.g., an SPSS, Excel, or SAS-file), and convert it to a data.frame. Then,
+# use the function open_data(your_data_frame) or closed_data(your_data_frame)
+# to store the data.
+
+library(worcs)
+library(foreign)
+library(ggplot2)
+library(tidySEM)
+df <- read.csv("MSRC LPA Data 1.6.21 NO IDs for LPA.csv", stringsAsFactors = FALSE)
+df[df == 888] <- NA
+
+desc <- descriptives(df)
+
+closed_data(df)

### 2021-01-31 codebook_df.Rmd
remove derived variables

@@
 ---
-title: "Codebook created on 2021-01-31 at 2021-01-31 09:50:03"
+title: "Codebook created on 2021-01-31 at 2021-01-31 09:51:38"
 output: github_document
@@
 ## Dataset description
-The data contains 1904 cases and 27 variables.
+The data contains 1904 cases and 21 variables.
 

### 2021-01-31 prepare_data.R
remove obsolete code

@@ -4,12 +4,10 @@
 # to store the data.
 
 library(worcs)
-library(foreign)
-library(ggplot2)
-library(tidySEM)
 df <- read.csv("MSRC LPA Data 1.6.21 NO IDs for LPA.csv", stringsAsFactors = FALSE)
 df[df == 888] <- NA
 
 desc <- descriptives(df)
 
 closed_data(df)
+

### 2021-02-06 codebook_df.Rmd
Use original data instead of cleaned

@@
 ---
-title: "Codebook created on 2021-01-31 at 2021-01-31 09:51:38"
+title: "Codebook created on 2021-02-06 at 2021-02-06 11:35:18"
 output: github_document
@@
 ## Dataset description
-The data contains 1904 cases and 21 variables.
+The data contains 2648 cases and 25 variables.
 

### 2021-02-06 manuscript/manuscript.Rmd
Use original data instead of cleaned

@@
 ---
-title: "Untitled"
+title: "Results MSRC latent class analysis"
 output: github_document
@@
 # (whichever is available), to allow anyone to reproduce your code:
-# load_data()
+load_data()
 knitr::opts_chunk$set(echo = TRUE)
@@
 This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency.
-All code <!--and data--> are available at <git@github.com:cjvanlissa/MSRC_LPA.git>.
-
-This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
+All code <!--and data--> are available at <https://github.com/cjvanlissa/MSRC_LPA>.
 
@@
 
-## GitHub Documents
+## Descriptive statistics
 
-This is an R Markdown format used for publishing markdown documents to GitHub.
-When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
+```{r}
+library(ggplot2)
+library(tidySEM)
+library(tidyLPA)
+desc <- descriptives(df)
 
-## Including Code
+use_vars <- c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", "CDE12", "SA_Freq_Rank", "NSSI_Freq_Rank")
 
-You can include R code in the document as follows:
+df_plot <- do.call(rbind, lapply(grep("^CD", use_vars, value = TRUE), function(x){data.frame(Variable = x, value = df[[x]])}))
 
-```{r cars}
-summary(cars)
+p_bar <- ggplot(df_plot, aes(x = value)) + 
+  geom_bar() +
+  facet_wrap(~Variable, scales = "free") +
+  theme_bw()
+
+ggsave("bar.png", device = "png", width = 200, height = 120, units = "mm", dpi = 300)
+
+df_plot <- do.call(rbind, lapply(grep("Freq", use_vars, value = TRUE), function(x){data.frame(Variable = x, value = df[[x]])}))
+
+df$NSSI_log <- log(df$NSSI_Freq_Rank+.0000001)
+df$SA_log <- log(df$SA_Freq_Rank+.0000001)
+df$NSSI_inv <- 1/(df$NSSI_Freq_Rank+.0000001)
+df$SA_inv <- 1/(df$SA_Freq_Rank+.0000001)
+df$NSSI_sqrt <- sqrt(df$NSSI_Freq_Rank)
+df$SA_sqrt <- sqrt(df$SA_Freq_Rank)
+df$NSSI_dummy <- as.numeric(df$NSSI_Freq_Rank == 0)
+df$SA_dummy <- as.numeric(df$SA_Freq_Rank == 0)
+df_plot <- do.call(rbind, lapply(grep("(NSSI|SA)", names(df), value = TRUE), function(x){
+  data.frame(Variable = paste0("Variable: ", gsub("^(.+?)_.*$", "\\1", x), " (", gsub("_", " ", gsub("^.+?_(.*)$", "\\1", x)), ")"), 
+             value = df[[x]])
+}))
+df_plot$Variable <- ordered(df_plot$Variable, levels = unique(df_plot$Variable))
+p_dens <- ggplot(df_plot, aes(x = value)) + 
+  geom_density() +
+  facet_wrap(~Variable, scales = "free", ncol = 2) +
+  theme_bw()
+
+ggsave("density.png", device = "png", width = 200, height = 350, units = "mm", dpi = 300)
+```
+
+## Analysis
+
+```{r model}
+
+# MSRC <- data[1:1905,] %>%
+#   select (CDE7_NEW, CDE8, CDE9, CDE10, CDE11, CDE12, SA_Freq_Rank, NSSI_Freq_Rank) %>%
+#   single_imputation() %>%
+#   estimate_profiles(1:10, variances="equal", covariances="zero")
+# 
+# MSRC
+# 
+# LPABest <- data[1:1905,] %>%
+#   select(CDE7_NEW, CDE8, CDE9, CDE10, CDE11, CDE12, SA_Freq_Rank, NSSI_Freq_Rank) %>%
+#   single_imputation() %>%
+#   estimate_profiles(9, variances="equal", covariances="zero")
+# get_fit(LPABest)
+# 
 ```

### 2021-02-06 mplus_functions.R

@@ -1,0 +1,147 @@
+library(MplusAutomation)
+library(tibble)
+lpa_model <- function(num, df_anal){
+  desc <- descriptives(df_anal)
+  browser()
+  cat_vars <- desc$name[desc$unique < 8 & desc$type %in% c("integer", "factor", "character")]
+  cont_vars <- desc$name[!desc$name %in% cat_vars]
+  mod <- mplusObject(
+    TITLE = paste0("Categorical only ", num, " classes"),
+    VARIABLE = paste0(
+      "CLASSES = c (", num, ");\n",
+      paste0("CATEGORICAL = ", paste0(cat_vars, collapse = "\n"), ";")),
+    ANALYSIS = "TYPE IS MIXTURE;\nLRTSTARTS = 0 0 40 10;",
+    OUTPUT = "TECH14;",
+    SAVEDATA = paste0("FILE IS dat_", num, ".dat;\nSAVE = CPROBABILITIES;"),
+    usevariables = names(df_anal),
+    rdata = df_anal
+  )
+}
+run_lpa <- function(classes, df_anal){
+  out <- lapply(classes, function(i){
+
+    mod <- lpa_model(i, df_anal)
+    res <- mplusModeler(mod,
+                        modelout = paste0("mod_", i, ".inp"),
+                        run = 1L)
+    make_outlist(res, this_model = NA, this_class = i, selected_variables = names(df_anal))
+  })
+  names(out) <- paste("model_", "unknown", "_class_", 
+                           classes, sep = "")
+  class(out) <- c("tidyLPA", "list")
+  out
+}
+
+make_outlist <- function(res, this_model = NA, this_class, selected_variables){
+  out <- list(model = res$results)
+  warnings <- NULL
+  if (!is.null(out$model$summaries$LL)) {
+    out$fit <- c(Model = this_model, Classes = this_class, 
+                 tidyLPA:::calc_fitindices(out$model))
+    estimates <- estimates(out$model)
+    if (!is.null(estimates)) {
+      estimates$Model <- this_model
+      estimates$Classes <- this_class
+    }
+    out$estimates <- estimates
+    if(!is.null(out$model[["savedata"]])) {
+      outdat <- as.matrix(out$model$savedata[, grep("CPROB1", 
+                                                    names(out$model$savedata)):ncol(out$model$savedata)])
+
+      
+      dff <- outdat
+      colnames(dff) <- c(paste0("CPROB", 1:(ncol(dff) - 
+                                              1)), "Class")
[…]

### 2021-02-06 prepare_data.R

@@ -4,10 +4,18 @@
 # to store the data.
 
 library(worcs)
-df <- read.csv("MSRC LPA Data 1.6.21 NO IDs for LPA.csv", stringsAsFactors = FALSE)
-df[df == 888] <- NA
+library(foreign)
+df <- read.spss("Goodman data 8_19 1.30.21 for Caspar.sav", to.data.frame = T)
+df$Sitecode <- factor(df$Sitecode)
+df$Gender <- droplevels(df$Gender_MF_Only)
+df$Education <- as.numeric(df$EducationJT)
+df$Method <- droplevels(df$CDE15_Method_Condensed_NEW)
+df$Branch <- factor(gsub("^(Army|Air Force|Navy|Marine Corps|Coast Guard).*$", "\\1", df$Military_Branch))
+df[c("ID", "Gender_MF_Only", "EducationJT", "CDE15_CODE", "CDE15_Method_Condensed_NEW", "CDE15_Method_Condensed", "CDE15_Method_More_Condensed", "Military_Branch")] <- NULL
+
+# Retain only cases with 1 attempt or more
+df <- df[which(df$CDE13 > 0), ]
 
 desc <- descriptives(df)
 
 closed_data(df)
-

### 2021-02-08 manuscript/manuscript.Rmd
Analyses first draft

--- 2021-01-31 manuscript/manuscript.Rmd
@@
 ---
-title: "Untitled"
-output: github_document
+title: "Results MSRC latent class analysis"
+output: bookdown::github_document2
 date: '`r format(Sys.time(), "%d %B, %Y")`'
@@
 library("worcs")
-# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
-# and end that file with either open_data(yourdata), or closed_data(yourdata).
-# Then, uncomment the line below to load the original or synthetic data
-# (whichever is available), to allow anyone to reproduce your code:
-# load_data()
-knitr::opts_chunk$set(echo = TRUE)
+source("../mplus_functions.R")
+knitr::opts_chunk$set(include = FALSE, echo = FALSE, message = FALSE, warning = FALSE, error = TRUE)
+options(knitr.kable.NA = '')
+run_everything <- FALSE
 ```
 
+**NOTE: I've written a first-glance interpretation of the results as a placeholder. Please interpret the results substantively at your own discretion.**
+
 This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency.
-All code <!--and data--> are available at <git@github.com:cjvanlissa/MSRC_LPA.git>.
-
-This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.
+All code <!--and data--> are available at <https://github.com/cjvanlissa/MSRC_LPA>.
 
@@
 
-## GitHub Documents
+## Descriptive statistics
 
-This is an R Markdown format used for publishing markdown documents to GitHub.
-When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
+```{r}
+library(ggplot2)
+library(tidySEM)
+library(tidyLPA)
+load_data()
+desc <- descriptives(df)
+# We're aiming to characterize profiles/classes based on the characteristics of suicide attempts (CDE7_NEW, CDE8, CDE9, CDE10, CDE11, CDE12, CDE13, CDE17).
 
-## Including Code
+indicators <- c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", 
+"CDE12", "CDE13","CDE17")
 
-You can include R code in the document as follows:
+p_trans <- transformations(df[c("CDE13", "CDE17")])
+# Note that due to the extreme censored nature of these variables, most variance is alreay described by a median split
 
-```{r cars}
-summary(cars)
+df$CDE13 <- as.integer(!df$CDE13 == 1)
+df$CDE17 <- as.integer(df$CDE17 == 0)
+
+# We're primarily interested in whether resulting profile membership is related to the method of suicide attempt used and the level of medical attention necessitated (our outcomes). 
+# CDE15_Method_Condensed_NEW (method)
+# CDE16 (medical attention necessitated).
+outcomes <- c("Method", "CDE16")
+
+# Auxiliary variables:  Age, Gender, Race, EducationJT, Any_Service. 
+aux <- c("Age", "Gender", "Race", "Education", "Any_Service")
+
+# c(
+# CDE7_NEW = "told_someone", 
+# CDE8 = "attempt", 
+# CDE9 = "fatal", 
+# CDE10 = "lethal", 
+# CDE11 = "intendie", 
+# CDE12 = "fixable", 
+# CDE13 = "times", 
+# CDE16 = "medical", 
+# CDE17 = "nssi"
+# )
+
+# CDE13: number of suicide attempts
+# CDE17: number of NSSI instances.
+
+df_plot <- data.frame(lapply(df[indicators], as.numeric))
+df_plot <- do.call(rbind, lapply(names(df_plot), function(x){data.frame(Variable = x, value = df_plot[[x]])}))
+
+p_bar <- ggplot(df_plot, aes(x = value)) + 
+  geom_bar() +
+  facet_wrap(~Variable, scales = "free") +
+  theme_bw()
+
+ggsave("bar.png", device = "png", width = 200, height = 120, units = "mm", dpi = 300)
+
 ```
 
-## Including Plots
+## Analysis
 
-You can also embed plots, for example:
+We conducted a latent class analysis for 1-7 classes in Mplus 8.4.
+All latent class indicators were coded as categorical.
+Class membership for categorical variables is determined by the proportion of responses in each category.
+We used tidyLPA to determine the optimum number of classes (see Table \@ref(tab:tabres)).
+According to the BIC, the model fit improved dramatically from a one-class solution to a two-class solution, and continued improving until a five-class solution.
+According to the bootstrapped likelihood ratio test, model fit improved significantly with an increasing number of classes.
+However, all solutions with more than two classes had low posterior classification probabilities (<= .77),
+and the smallest class contained only approximately 10% of all cases.
+We thus selected a two-class solution for our final analysis.
+Note that the entropy for all models is low, which indicates that classes are not clearly separable.
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r numclasses}
+if(run_everything){
+  df_anal <- df[indicators]
+  res <- run_lpa(1:7, df_anal)
+  saveRDS(res, "res1-7.RData")
+} else {
+  res <- readRDS("res1-7.RData")
+}
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r tabres, include = TRUE, results="asis"}
+tab <- get_fit(res)[,c("Classes", "AIC", "BIC", "Entropy", "prob_min", "prob_max", "n_min", "n_max", "BLRT_p")]
+write.csv(tab, "tab_numclasses.csv", row.names = FALSE)
+knitr::kable(tab, digits = 2, caption = "Fit of latent class models")
+```
+
+## Final model
+
+For all indicator variables, the proportion of responses by response category and latent class are displayed in Figure \@ref(fig:figpresprob). 
+These same results are rescaled to the approximate number of participants per class (based on summed posterior class probabilities) in Figure \@ref(fig:figpres).
+Both figures show that participants in the first class were relatively more likely to report higher scores on being certain that their attempt would be fatal and lethal, intent to die, and a belief that their attempt could not be fixed by medical attention, as compared to participants in the second class.
+Participants in the first class were relatively less likely to report a history of NSSI.
+
+```{r figpresprob, include = TRUE, fig.cap="Results of the two-class latent class model. Proportion of responses by response category and latent class."}
+library(ggplot2)
+df_plot <- res$model_unknown_class_2$model$parameters$probability.scale
+df_plot$Frequency <- res$model_unknown_class_2$model$class_counts$posteriorProb$count[as.integer(df_plot$LatentClass)] * df_plot$est
+names(df_plot) <- c("Variable", "Category", "est", "se", "est_se", "pval", "Class", "Frequency")
+
+rename_vars <- c(
+CDE7_NEW = "Told someone",
+CDE8 = "Will likely attempt",
+CDE9 = "Certain fatal",
+CDE10 = "Certain lethal",
+CDE11 = "Intended to die",
+CDE12 = "Could be fixed",
+CDE13 = "Attempts",
+CDE16 = "Medical attention (DV)",
+CDE17 = "NSSI",
+AGE = "Age (cov)",
+EDUCATION = "Education (cov)",
+GENDER = "Gender (cov)",
+ANY_SERVICE = "Service (cov)",
+METHOD = "Method (DV)",
+RACE = "Race (cov)"
+)
+df_plot$Variable <- ordered(df_plot$Variable, 
+                            levels = unique(df_plot$Variable),
+                            labels = rename_vars[unique(df_plot$Variable)])
+
+p_res_prob <- ggplot(df_plot, aes(x = Class, y = est, fill = Category)) + geom_bar(stat = "identity", position = position_fill(reverse = TRUE)) + facet_wrap(~Variable, nrow = 4, scales = "free") + ylab(NULL) + theme_bw()# + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
+ggsave("p_res_prob.png", device = "png", width = 200, height = 180, units = "mm", dpi = 300)
+p_res_prob
+```
+
+```{r figpres, include = TRUE, fig.cap="Results of the two-class latent class model.
+Proportion of responses by response category and latent class, rescaled to the number of participants per latent class (based on posterior class probability)."}
+p_res <- ggplot(df_plot, aes(x = Category, y = Frequency, fill = Class)) + geom_bar(stat = "identity", position = position_stack(reverse = TRUE)) + facet_wrap(~Variable, nrow = 4, scales = "free_x") + xlab(NULL) + theme_bw()
+ggsave("p_res.png", device = "png", width = 200, height = 180, units = "mm", dpi = 300)
+p_res
+```
+
+## Auxiliary variables
+
+```{r mplusmodel}
+aux_cat <- c("Gender", "Race", "Any_Service", "Method")
+  aux_cont <- c("Age", "Education", "CDE16")
+  df_anal <- df[c(indicators, aux_cat, aux_cont)]
+  cat_dict <- lapply(df_anal[aux_cat], levels)
+  df_anal[aux_cat] <- lapply(df_anal[aux_cat], as.integer)
+  cat_vars <- c("CDE7_NEW", "CDE8",
+                "CDE9", "CDE10", "CDE11", "CDE12", "CDE13", 
+                "CDE17")
+if(run_everything){
+  mod_cont <- mplusObject(
+    TITLE = paste0("2 class with auxiliary continuous"),
+    VARIABLE = paste0("CLASSES = c (2);\n",
+                      paste0("CATEGORICAL = \n", paste0(cat_vars, collapse = "\n"), ";\n"),
+                      paste0("USEVARIABLES = \n", paste0(indicators, collapse = "\n"), ";\n"),
+                      paste0(c("AUXILIARY = \n",
+                               paste0(aux_cont, " (BCH)\n"),
+                               #paste0(aux_cat, " (DCATEGORICAL)\n"),
+                               ";\n"), collapse = "")),
+    ANALYSIS = "TYPE IS MIXTURE;\nLRTSTARTS = 0 0 40 10;\nOPTSEED = 637345;\n",
+    OUTPUT = "TECH14;",
+    SAVEDATA = paste0("FILE IS dat_2_aux_cont.dat;\nSAVE = CPROBABILITIES;"),
+    usevariables = names(df_anal),
+    rdata = df_anal
+  )
+
+  res_cont <- mplusModeler(mod_cont,
+                           modelout = paste0("mod_2_aux_cont.inp"),
+                           run = 1L)$results
+
+  mod_cat <- mplusObject(
+    TITLE = paste0("2 class with auxiliary categorical"),
+    VARIABLE = paste0("CLASSES = c (2);\n",
+                      paste0("CATEGORICAL = \n", paste0(cat_vars, collapse = "\n"), ";\n"),
+                      paste0("USEVARIABLES = \n", paste0(indicators, collapse = "\n"), ";\n"),
+                      paste0(c("AUXILIARY = \n",
+                               #paste0(aux_cont, " (BCH)\n"),
+                               paste0(aux_cat, " (DCATEGORICAL)\n"),
+                               ";\n"), collapse = "")),
+    ANALYSIS = "TYPE IS MIXTURE;\nLRTSTARTS = 0 0 40 10;\nOPTSEED = 637345;\n",
+    OUTPUT = "TECH14;",
+    SAVEDATA = paste0("FILE IS dat_2_aux_cat.dat;\nSAVE = CPROBABILITIES;"),
+    usevariables = names(df_anal),
+    rdata = df_anal
+  )
+
+  mplusModeler(mod_cat,
+               modelout = paste0("mod_2_aux_cat.inp"),
+               run = 0L)
+  runModels("mod_2_aux_cat.inp")
+  res_cat <- extract_cat_tests(readLines("mod_2_aux_cat.out"))
+} else {
+  res_cont <- readModels("mod_2_aux_cont.out")
+  res_cat <- extract_cat_tests(readLines("mod_2_aux_cat.out"))
+}
+```
+
+We were interested in whether these classes differed on two outcome variables
+and several covariates.
+To prevent the inclusion of these auxiliary variables from influencing the latent class measurement model,
+we used the three-step method described by @asparouhovAuxiliaryVariablesMixture2014.
+Results for continuous auxiliary variables are displayed in Table \@ref(tab:tabcont),
+and results for categorical auxiliary variables are displayed in Table \@ref(tab:tabcat).
+All auxiliary variables differed significantly across the two classes.
+
+With regard to the method of the attempt,
+the most notable differences between the classes were that the first class was more likely than the second to report shooting as a method,
+and the second class was more likely than the first to report cutting as a method.
+With regard to the amount of medical attention required, the first class scored significantly higher than the second.
+
+With regard to the covariates, the first class consisted of a relatively larger proportion of males than the second class.
+The first class was significantly older and lower educated than the second.
+The first class was relatively more likely to be currently serving or a veteran, whereas the second class was relatively more likely to have no military service record.
+Although there was a significant association between class membership and race, the chi square value was small, and no clear pattern emerged from the results.
+
+```{r tabcont, include = TRUE}
+tab <- res_cont$lcCondMeans$overall
+tab$var <- rename_vars[tab$var]
+tab$df <- NULL
+names(tab)[1] <- "Variable"
+tab <- tab[c(grep("(DV)", tab$Variable), grep("(cov)", tab$Variable)), ]
+rownames(tab) <- NULL
+knitr::kable(tab, digits = 2, caption = "Class differences in continuous auxiliary variables.")
+```
+
+```{r tabcat, include = TRUE}
+ct_dct <- cat_dict
+names(ct_dct) <- toupper(names(ct_dct))
+
+cats <- do.call(rbind, lapply(c("METHOD", "GENDER", "RACE", "ANY_SERVICE"), function(thename){
+  x <- res_cat[[thename]]
+  out <- x$parameters[, c("Class", "Category", "Prob")]
+  out <- reshape(out, v.names = "Prob", timevar = "Class", idvar = "Category", direction = "wide")
+  out$chisq <- NA
+  out$p <- NA
+  out$chisq[1] <- x$tests$Chi.square
+  out$p[1] <- x$tests$p
+  out <- cbind(Variable = NA, out)
+  out$Variable[1] <- thename
+  out$Category <- ct_dct[[thename]][out$Category]
+  out
+}))
+cats$Variable <- rename_vars[cats$Variable]
+rownames(cats) <- NULL
+knitr::kable(cats, digits = 2, caption = "Class differences in categorical auxiliary variables.")
+```
+
+```{r figcont, include = TRUE}
+tab <- res_cont$lcCondMeans$overall
+tab$var <- rename_vars[tab$var]
+tab$df <- NULL
+names(tab)[1] <- "Variable"
+tab <- tab[c(grep("(DV)", tab$Variable), grep("(cov)", tab$Variable)), ]
+rownames(tab) <- NULL
+knitr::kable(tab, digits = 2, caption = "Class differences in continuous auxiliary variables.")
+```
+
+```{r tabcat, include = TRUE}
+ct_dct <- cat_dict
+names(ct_dct) <- toupper(names(ct_dct))
+
+cats <- do.call(rbind, lapply(c("METHOD", "GENDER", "RACE", "ANY_SERVICE"), function(thename){
+  x <- res_cat[[thename]]
+  out <- x$parameters[, c("Class", "Category", "Prob")]
+  out <- reshape(out, v.names = "Prob", timevar = "Class", idvar = "Category", direction = "wide")
+  out$chisq <- NA
+  out$p <- NA
+  out$chisq[1] <- x$tests$Chi.square
+  out$p[1] <- x$tests$p
+  out <- cbind(Variable = NA, out)
+  out$Variable[1] <- thename
+  out$Category <- ct_dct[[thename]][out$Category]
+  out
+}))
+cats$Variable <- rename_vars[cats$Variable]
+rownames(cats) <- NULL
+knitr::kable(cats, digits = 2, caption = "Class differences in categorical auxiliary variables.")
+```

### 2021-02-08 mplus_functions.R

@@ -2,8 +2,8 @@ library(MplusAutomation)
 library(tibble)
 lpa_model <- function(num, df_anal){
   desc <- descriptives(df_anal)
-  browser()
-  cat_vars <- desc$name[desc$unique < 8 & desc$type %in% c("integer", "factor", "character")]
+  #browser()
+  cat_vars <- desc$name[desc$unique < 9 & desc$type %in% c("integer", "factor", "character")]
   cont_vars <- desc$name[!desc$name %in% cat_vars]
   mod <- mplusObject(
     TITLE = paste0("Categorical only ", num, " classes"),
@@ -144,4 +144,46 @@ transformations <- function(df){
     facet_wrap(~transformation, scales = "free", ncol = length(vars)) +
     theme_bw() +
     scale_y_continuous(labels = NULL)
+}
+
+
+extract_cat_tests <- function(txt){
+  start <- grep("EQUALITY TESTS OF MEANS/PROBABILITIES ACROSS CLASSES", txt, fixed = TRUE)
+  end <- grep("TECHNICAL 14 OUTPUT", txt, fixed = TRUE)-1
+  txt <- txt[start:end]
+  txt <- txt[!txt == ""]
+  sections <- which(!grepl(" ", txt, fixed = TRUE))
+  out <- mapply(function(st, en){
+    thetxt <- txt[st:en]
+    props <- thetxt[grepl("Class", thetxt, fixed = TRUE) | grepl("Category", thetxt, fixed = TRUE) ]
+    props <- strsplit(props, "\\s+")
+    lengths <- sapply(props, length)
+    labs <- sapply(props[lengths == 3], `[`, 3)
+    props <- data.frame(do.call(rbind, props[lengths == 9]))
+    props$X3 <- as.integer(props$X3)
+    which_lab <- 1
+    props$X1[1] <- labs[which_lab]
+    for(i in 2:nrow(props)){
+      if(!sign(props$X3[i]-props$X3[i-1] > 0)){
+        which_lab <- which_lab + 1
+      }
+      props$X1[i] <- labs[which_lab]
+    }
+    names(props) <- c("Class", "X2", "Category", "Prob", "se", "OR", "se_OR", "ci.lower", "ci.upper")
+    props <- props[, -2]
+    
+    tests <- thetxt[grepl("Overall test", thetxt, fixed = TRUE) | grepl(" vs. ", thetxt, fixed = TRUE) ]
[…]

### 2021-02-08 prepare_data.R

@@ -12,6 +12,7 @@ df$Education <- as.numeric(df$EducationJT)
 df$Method <- droplevels(df$CDE15_Method_Condensed_NEW)
 df$Branch <- factor(gsub("^(Army|Air Force|Navy|Marine Corps|Coast Guard).*$", "\\1", df$Military_Branch))
 df[c("ID", "Gender_MF_Only", "EducationJT", "CDE15_CODE", "CDE15_Method_Condensed_NEW", "CDE15_Method_Condensed", "CDE15_Method_More_Condensed", "Military_Branch")] <- NULL
+df[c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", "CDE12", "CDE16")] <- lapply(df[c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", "CDE12", "CDE16")], as.integer)
 
 # Retain only cases with 1 attempt or more
 df <- df[which(df$CDE13 > 0), ]

### 2021-02-08 manuscript/manuscript.Rmd
re-render rmd

@@
 
-```{r figcont, include = TRUE}
+```{r figcont, eval = FALSE}
 tab <- res_cont$lcCondMeans$overall
@@
 
-```{r tabcat, include = TRUE}
+```{r figcat, eval = FALSE}
 ct_dct <- cat_dict

### 2021-02-15 codebook_df.Rmd
Analyses first draft
exclude participants for whom it's unclear whether they are currently serving

@@
 ---
-title: "Codebook created on 2021-02-06 at 2021-02-06 11:35:18"
+title: "Codebook created on 2021-02-15 at 2021-02-15 10:15:54"
 output: github_document
@@
 ## Dataset description
-The data contains 2648 cases and 25 variables.
+The data contains 2411 cases and 25 variables.
 

### 2021-02-15 manuscript/manuscript.Rmd
exclude participants for whom it's unclear whether they are currently serving

@@
 load_data()
+
 desc <- descriptives(df)

### 2021-02-15 prepare_data.R

@@ -6,6 +6,9 @@
 library(worcs)
 library(foreign)
 df <- read.spss("Goodman data 8_19 1.30.21 for Caspar.sav", to.data.frame = T)
+
+# 3. Military Service Auxiliary Variable - Can you please remove/exclude from analyses the participants for whom it's unclear whether they are currently (vs. previously) serving when looking at military service as an auxiliary variable?
+df <- df[!df$Any_Service == "served but unclear if still serving (cougle)", ]
 df$Sitecode <- factor(df$Sitecode)
 df$Gender <- droplevels(df$Gender_MF_Only)
 df$Education <- as.numeric(df$EducationJT)

### 2021-02-15 manuscript/manuscript.Rmd
Add explanation for dichotomization

@@
 
+```
+
+We present descriptive statistics of the observed variables below (see Table \@ref(tab:tabdesc)).
+Two of the latent class indicators,
+NSSI history and suicide attempt frequency,
+were measured at a continuous level of measurement.
+However, these variables were censored and positively skewed in the extreme,
+such that $`r round(100*prop.table(table(df[["CDE13"]]))[1])`\%$ of participants reported the lowest level of NSSI, and $`r round(100*prop.table(table(df[["CDE17"]]))[1])`\%$ of participants reported the lowest level of suicide attempts.
+Based on a visual comparison of transformations for skewed variables (square root, log, inverse, rank-ordering, and median dichotomization),
+it was observed that most transformations split the sample into this lowest category versus all other response levels.
+This indicates that, despite the continuous measurement scale, these variables convey information at the binary level.
+We thus used median dichotomization to account for the deviation from normality,
+and treated these dichotomized variables as ordinal.
+This is a validated approach for dealing with severely censored variables (Muthén & Speckart, 1983).
+
+```{r tabdesc, results = "asis"}
+knitr::kable(desc, caption = "Descriptive statistics")
 ```

### 2021-02-15 manuscript/manuscript.Rmd
Finalize results

@@
 # Note that due to the extreme censored nature of these variables, most variance is alreay described by a median split
+props <- c(round(100*prop.table(table(df[["CDE13"]]))[1]),
+           round(100*prop.table(table(df[["CDE17"]]))[1]))
 
@@
 However, these variables were censored and positively skewed in the extreme,
-such that $`r round(100*prop.table(table(df[["CDE13"]]))[1])`\%$ of participants reported the lowest level of NSSI, and $`r round(100*prop.table(table(df[["CDE17"]]))[1])`\%$ of participants reported the lowest level of suicide attempts.
+such that $`r props[1]`\%$ of participants reported the lowest level of NSSI, and $`r props[2]`\%$ of participants reported the lowest level of suicide attempts.
 Based on a visual comparison of transformations for skewed variables (square root, log, inverse, rank-ordering, and median dichotomization),
@@
 and treated these dichotomized variables as ordinal.
-This is a validated approach for dealing with severely censored variables (Muthén & Speckart, 1983).
+This is a validated approach for dealing with severely censored variables [@muthenCategorizingSkewedLimited1983].
 
-```{r tabdesc, results = "asis"}
+```{r tabdesc, include = TRUE, results = "asis"}
 knitr::kable(desc, caption = "Descriptive statistics")
@@
               "CDE17")
+
+  # Create dummies for all categories to get by-category comparisons
+  df_dum <- df[c(indicators, aux_cat, aux_cont)]
+  dum_vars <- aux_cat[sapply(df_dum[aux_cat], function(x){length(unique(na.omit(x)))}) > 2]
+  the_opt <- getOption("na.action")
+  options(na.action='na.pass')
+  dummies <- model.matrix(as.formula(paste0("~ -1 + ", paste0(dum_vars, collapse = " + "))), df_dum,
+                          contrasts.arg = lapply(df_dum[dum_vars], contrasts, contrasts=FALSE))
+
+  dummies <- data.frame(dummies, check.names = FALSE)
+  options(na.action=the_opt)
+  for(i in dum_vars){
+    names(dummies) <- gsub(paste0("^", i, "(?!Other)"), "", names(dummies), perl = TRUE)
+  }
+  dummie_dict <- gsub("^.+?Other", "Other", names(dummies))
+  names(dummies) <- gsub("[ /\\(].*", "", names(dummies))
+  df_dum <- cbind(df_dum, dummies)
 if(run_everything){
@@
   res_cat <- extract_cat_tests(readLines("mod_2_aux_cat.out"))
+
+  mod_catdum <- mplusObject(
+    TITLE = paste0("2 class with auxiliary categorical dummies"),
+    VARIABLE = paste0("CLASSES = c (2);\n",
+                      paste0("CATEGORICAL = \n", paste0(cat_vars, collapse = "\n"), ";\n"),
+                      paste0("USEVARIABLES = \n", paste0(indicators, collapse = "\n"), ";\n"),
+                      paste0(c("AUXILIARY = \n",
+                               #paste0(aux_cont, " (BCH)\n"),
+                               paste0(names(dummies), " (DCATEGORICAL)\n"),
+                               ";\n"), collapse = "")),
+    ANALYSIS = "TYPE IS MIXTURE;\nLRTSTARTS = 0 0 40 10;\nOPTSEED = 637345;\n",
+    OUTPUT = "TECH14;",
+    SAVEDATA = paste0("FILE IS dat_2_aux_catdum.dat;\nSAVE = CPROBABILITIES;"),
+    usevariables = c(names(df_anal), names(dummies)),
+    rdata = df_dum
+  )
+
+  mplusModeler(mod_catdum,
+               modelout = paste0("mod_2_aux_catdum.inp"),
+               run = 0L)
+  runModels("mod_2_aux_catdum.inp")
+  res_catdum <- extract_cat_tests(readLines("mod_2_aux_catdum.out"))
+
 } else {
@@
   res_cat <- extract_cat_tests(readLines("mod_2_aux_cat.out"))
+  res_catdum <- extract_cat_tests(readLines("mod_2_aux_catdum.out"))
+  names(res_catdum) <- dummie_dict
 }
@@
 cats$Variable <- rename_vars[cats$Variable]
+cats[["p 1 vs 2"]] <- sapply(res_catdum, function(x){x$tests$p[1]})[match(cats$Category, dummie_dict)]
 rownames(cats) <- NULL
@@
 rownames(cats) <- NULL
+
 knitr::kable(cats, digits = 2, caption = "Class differences in categorical auxiliary variables.")

### 2021-06-07 manuscript/manuscript.Rmd
update results

@@
 METHOD = "Method (DV)",
-RACE = "Race (cov)"
+RACE = "Race (cov)",
+CARE_CAT = "Medical attention cat (DV)"
 )
@@
 ```{r mplusmodel}
-aux_cat <- c("Gender", "Race", "Any_Service", "Method")
+df$care_cat <- factor(df$CDE16)
+aux_cat <- c("Gender", "Race", "Any_Service", "Method", "care_cat")
 aux_cont <- c("Age", "Education", "CDE16")
@@
   # Create dummies for all categories to get by-category comparisons
-  df_dum <- df[c(indicators, aux_cat, aux_cont)]
+  df_dum <- df_anal[c(indicators, aux_cat, aux_cont)]
+  df_dum <- data.frame(lapply(df_dum, as.factor))
   dum_vars <- aux_cat[sapply(df_dum[aux_cat], function(x){length(unique(na.omit(x)))}) > 2]
+
   the_opt <- getOption("na.action")
@@
   dummies <- model.matrix(as.formula(paste0("~ -1 + ", paste0(dum_vars, collapse = " + "))), df_dum,
-                          contrasts.arg = lapply(df_dum[dum_vars], contrasts, contrasts=FALSE))
+                          contrasts.arg = lapply(df_dum[dum_vars], contrasts, contrasts = FALSE))
 
@@
   options(na.action=the_opt)
-  for(i in dum_vars){
-    names(dummies) <- gsub(paste0("^", i, "(?!Other)"), "", names(dummies), perl = TRUE)
-  }
-  dummie_dict <- gsub("^.+?Other", "Other", names(dummies))
-  names(dummies) <- gsub("[ /\\(].*", "", names(dummies))
+  names(dummies)[nchar(names(dummies)) > 8] <- paste0(
+    substr(names(dummies)[nchar(names(dummies)) > 8], 1, 7),
+    sub('.*(?=.$)', '', names(dummies)[nchar(names(dummies)) > 8], perl=T)
+  )
+
+  # for(i in dum_vars){
+  #   names(dummies) <- gsub(paste0("^", i, "(?!Other)"), "", names(dummies), perl = TRUE)
+  # }
+  #dummie_dict <- gsub("^.+?Other", "Other", names(dummies))
+  #names(dummies) <- gsub("[ /\\(].*", "", names(dummies))
   df_dum <- cbind(df_dum, dummies)
@@
                            run = 1L)$results
-
+  #df_anal$Any_Service <- droplevels()
   mod_cat <- mplusObject(
@@
   res_cont <- readModels("mod_2_aux_cont.out")
-  res_cat <- extract_cat_tests(readLines("mod_2_aux_cat.out"))
+  #res_cat <- extract_cat_tests(readLines("mod_2_aux_cat.out"))
+  res_cat <- readModels("mod_2_aux_cat.out")$lcCondMeans
   res_catdum <- extract_cat_tests(readLines("mod_2_aux_catdum.out"))
-  names(res_catdum) <- dummie_dict
+  #names(res_catdum) <- dummie_dict
 }
@@
 tab <- res_cont$lcCondMeans$overall
+tab$ci1 <- tidySEM::conf_int(tab$m.1, se = tab$se.1)
+tab$ci2 <- tidySEM::conf_int(tab$m.2, se = tab$se.2)
+tab$CramersV <- sqrt((as.numeric(tab$chisq)/res_cont$summaries$Observations)/1)
 tab$var <- rename_vars[tab$var]
@@
 rownames(tab) <- NULL
+tab <- tab[, c("Variable", "m.1", "se.1", "ci1", "m.2", "se.2", "ci2","chisq", "p")]
 knitr::kable(tab, digits = 2, caption = "Class differences in continuous auxiliary variables.")
@@
 names(ct_dct) <- toupper(names(ct_dct))
-
-cats <- do.call(rbind, lapply(c("METHOD", "GENDER", "RACE", "ANY_SERVICE"), function(thename){
+#c("METHOD", "GENDER", "RACE", "ANY_SERVICE")
+cats <- do.call(rbind, lapply(names(res_cat), function(thename){
   x <- res_cat[[thename]]
-  out <- x$parameters[, c("Class", "Category", "Prob")]
-  out <- reshape(out, v.names = "Prob", timevar = "Class", idvar = "Category", direction = "wide")
+  out <- x$parameters[, c("class", "category", "prob", "se")]
+  out$ci <- tidySEM::conf_int(as.numeric(out$prob), se = as.numeric(out$se))
+  out <- reshape(out, v.names = c("prob", "se", "ci"), timevar = "class", idvar = "category", direction = "wide")
   out$chisq <- NA
   out$p <- NA
-  out$chisq[1] <- x$tests$Chi.square
+  out$cramersv <- NA
+  out$chisq[1] <- x$tests$chi_square
   out$p[1] <- x$tests$p
+  the_n <- x$tests$n
+  if(is.null(the_n)) the_n <- res_cont$summaries$Observations
+  out$cramersv[1] <- sqrt((as.numeric(x$tests$chi_square)/as.numeric(the_n))/1)
   out <- cbind(Variable = NA, out)
   out$Variable[1] <- thename
-  out$Category <- ct_dct[[thename]][out$Category]
+  out$category <- ct_dct[[thename]][out$category]
   out
 }))
+test_res <- sapply(res_catdum, function(x){x$tests$p[1]})
+names_testres <- unique(gsub(".$", "", names(test_res)))
+test_res <- lapply(names_testres, function(x){test_res[grep(x, names(test_res))]})
+names(test_res) <- names_testres
+#test_res <- test_res[na.omit(pmatch(na.omit(cats$Variable), names(test_res)))]
+
+cats[["p 1 vs 2"]] <- NA
+for(i in names(test_res)){
+  #i = names(test_res)[1]
+  cats$`p 1 vs 2`[grep(i, cats$Variable):(grep(i, cats$Variable) + (length(test_res[[i]])-1))] <- test_res[[i]]
+}  
 cats$Variable <- rename_vars[cats$Variable]
-cats[["p 1 vs 2"]] <- sapply(res_catdum, function(x){x$tests$p[1]})[match(cats$Category, dummie_dict)]
+  #sapply(res_catdum, function(x){x$tests$p[1]})[match(cats$Category, dummie_dict)]
 rownames(cats) <- NULL

### 2021-06-07 manuscript/manuscript.Rmd
update

@@
 options(knitr.kable.NA = '')
-run_everything <- FALSE
+run_everything <- TRUE
 ```
@@
 "CDE12", "CDE13","CDE17")
-
+#df <- df[rowSums(is.na(df[, indicators])) == 0, ]
 p_trans <- transformations(df[c("CDE13", "CDE17")])
@@
 tab <- tab[, c("Variable", "m.1", "se.1", "ci1", "m.2", "se.2", "ci2","chisq", "p")]
+write.csv(tab, "classdiff_cont.csv", row.names = FALSE)
 knitr::kable(tab, digits = 2, caption = "Class differences in continuous auxiliary variables.")
@@
 rownames(cats) <- NULL
+write.csv(cats, "classdiff_cat.csv", row.names = FALSE)
 knitr::kable(cats, digits = 2, caption = "Class differences in categorical auxiliary variables.")

### 2021-06-07 manuscript/manuscript.Rmd
comment out n

@@
   out$cramersv <- NA
+  #out$n <- NA
   out$chisq[1] <- x$tests$chi_square

### 2021-06-07 manuscript/manuscript.Rmd
update

@@
 options(knitr.kable.NA = '')
-run_everything <- TRUE
+run_everything <- FALSE
 ```

### 2021-06-12 codebook_df.Rmd
update analyses

@@
 ---
-title: "Codebook created on 2021-02-15 at 2021-02-15 10:15:54"
+title: "Codebook created on 2021-06-11 at 2021-06-11 08:13:01"
 output: github_document
@@
 ## Dataset description
-The data contains 2411 cases and 25 variables.
+The data contains 2643 cases and 25 variables.
 

### 2021-06-12 prepare_data.R

@@ -5,20 +5,28 @@
 
 library(worcs)
 library(foreign)
+library(haven)
 df <- read.spss("Goodman data 8_19 1.30.21 for Caspar.sav", to.data.frame = T)
+# Retain only cases with 1 attempt or more
+df$exclude <- 0
+df$exclude[which(df$CDE13 > 0)] <- 1
 
 # 3. Military Service Auxiliary Variable - Can you please remove/exclude from analyses the participants for whom it's unclear whether they are currently (vs. previously) serving when looking at military service as an auxiliary variable?
-df <- df[!df$Any_Service == "served but unclear if still serving (cougle)", ]
+df$exclude[df$Any_Service == "served but unclear if still serving (cougle)"] <- 0
+filter_for_emily <- df
+filter_for_emily <- filter_for_emily[, c("Sitecode", "ID", "exclude")]
+haven::write_sav(filter_for_emily, "filter_for_emily.sav")
+df <- df[df$exclude == 1, ]
+df["exclude"] <- NULL
 df$Sitecode <- factor(df$Sitecode)
 df$Gender <- droplevels(df$Gender_MF_Only)
 df$Education <- as.numeric(df$EducationJT)
 df$Method <- droplevels(df$CDE15_Method_Condensed_NEW)
 df$Branch <- factor(gsub("^(Army|Air Force|Navy|Marine Corps|Coast Guard).*$", "\\1", df$Military_Branch))
+
 df[c("ID", "Gender_MF_Only", "EducationJT", "CDE15_CODE", "CDE15_Method_Condensed_NEW", "CDE15_Method_Condensed", "CDE15_Method_More_Condensed", "Military_Branch")] <- NULL
 df[c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", "CDE12", "CDE16")] <- lapply(df[c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", "CDE12", "CDE16")], as.integer)
 
-# Retain only cases with 1 attempt or more
-df <- df[which(df$CDE13 > 0), ]
 
 desc <- descriptives(df)
 

### 2021-06-12 prepare_data.R
update 2021-06-12 12:14:00

@@ -10,6 +10,9 @@ df <- read.spss("Goodman data 8_19 1.30.21 for Caspar.sav", to.data.frame = T)
 # Retain only cases with 1 attempt or more
 df$exclude <- 0
 df$exclude[which(df$CDE13 > 0)] <- 1
+# which(rowSums(is.na(df[c("CDE7_NEW", "CDE8", "CDE9", "CDE10", "CDE11", 
+#                          "CDE12", "CDE13","CDE17")])) == 8)
+#df$exclude <- 0
 
 # 3. Military Service Auxiliary Variable - Can you please remove/exclude from analyses the participants for whom it's unclear whether they are currently (vs. previously) serving when looking at military service as an auxiliary variable?
 df$exclude[df$Any_Service == "served but unclear if still serving (cougle)"] <- 0

### 2021-11-10 manuscript/manuscript.Rmd
Change figure based on reviewer comment

@@
 
+df_plot$Class <- ordered(df_plot$Class, levels = c("1", "2"), labels = c("Higher-Risk History", "Lower-Risk History"))
+df_attempt <- df_plot[df_plot$Variable == "Will likely attempt", ]
+df_plot <- df_plot[!df_plot$Variable == "Will likely attempt", ]
 p_res_prob <- ggplot(df_plot, aes(x = Class, y = est, fill = Category)) + geom_bar(stat = "identity", position = position_fill(reverse = TRUE)) + facet_wrap(~Variable, nrow = 4, scales = "free") + ylab(NULL) + theme_bw()# + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
@@
 p_res_prob
+```
+
+```{r figpresprob2, include = TRUE, fig.cap="Results of the two-class latent class model for future attempts. Proportion of responses by response category and latent class."}
+p_res_prob2 <- ggplot(df_attempt, aes(x = Class, y = est, fill = Category)) + geom_bar(stat = "identity", position = position_fill(reverse = TRUE)) + ylab(NULL) + theme_bw()# + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
+ggsave("p_res_prob2.png", device = "png", width = 200, height = 180, units = "mm", dpi = 300)
+p_res_prob2
 ```
